---
title: "OKC Technical Assessment"
author: "Jackson Taylor"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
SHOW_SOLUTIONS = FALSE
library(rlang)
```

For Team A, what percentage of their shots were attempted in the 2PT zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q5}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamA <- filter(shots.df, team == "Team A")
sizeA <- nrow(TeamA)
sizeATwoPt <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(x <= 22 & z <= 23.75) {
      sizeATwoPt <- sizeATwoPt + 1
    } 
}

APercentage2PT <- sizeATwoPt / sizeA
round(APercentage2PT, digits = 3)
```
APercentage2PT = 0.693

For Team A, what percentage of their shots were attempted in the NC3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q6}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamA <- filter(shots.df, team == "Team A")
sizeA <- nrow(TeamA)
sizeA_NC3 <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y > 7.8) {
      sizeA_NC3 <- sizeA_NC3 + 1
    } 
}

APercentageNC3 <- sizeA_NC3 / sizeA
round(APercentageNC3, digits = 3)
```
APercentageNC3 = 0.243

For Team A, what percentage of their shots were attempted in the C3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q7}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamA <- filter(shots.df, team == "Team A")
sizeA <- nrow(TeamA)
sizeA_C3 <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y < 7.8) {
      sizeA_C3 <- sizeA_C3 + 1
    } 
}

APercentageC3 <- sizeA_C3 / sizeA
round(APercentageC3, digits = 3)
```
APercentageC3 = 0.007

For Team A, what was the eFG in the 2PT zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q8}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamA <- filter(shots.df, team == "Team A")
sizeA <- nrow(TeamA)
sizeATwoPt <- 0
#Could just include the two point field goals variable from Q5 here, but so the code chunk stands alone I will include this code again for this question
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(x <= 22 & z <= 23.75) {
      sizeATwoPt <- sizeATwoPt + 1
    } 
}

sizeA2PTfgmade <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  fgmade <- TeamA[row, "fgmade"]
  z <- sqrt(x^2 + y^2)
  if(x <= 22 & z <= 23.75 & fgmade == 1) {
      sizeA2PTfgmade <- sizeA2PTfgmade + 1
    } 
}

APercentage2PT_Made <- sizeA2PTfgmade / sizeATwoPt
round(APercentage2PT_Made, digits = 3)
```
APercentage2PT_Made = 0.49

For Team A, what was the eFG in the NC3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q9}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamA <- filter(shots.df, team == "Team A")
sizeA <- nrow(TeamA)
#Could just include the NC3 field goals variable from Q6 here, but so the code chunk stands alone I will include this code again for this question
sizeA_NC3 <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y > 7.8) {
      sizeA_NC3 <- sizeA_NC3 + 1
    } 
}

sizeA_NC3fgmade <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  fgmade <- TeamA[row, "fgmade"]
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y > 7.8 & fgmade == 1) {
      sizeA_NC3fgmade <- sizeA_NC3fgmade + 1
    } 
}

APercentageNC3_Made <- sizeA_NC3fgmade / sizeA_NC3
round(APercentageNC3_Made, digits = 3)
```
APercentageNC3_Made = 0.309

For Team A, what was the eFG in the C3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q10}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamA <- filter(shots.df, team == "Team A")
sizeA <- nrow(TeamA)
#Could just include the C3 field goals variable from Q7 here, but so the code chunk stands alone I will include this code again for this question
sizeA_C3 <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y < 7.8) {
      sizeA_C3 <- sizeA_C3 + 1
    } 
}

sizeA_C3fgmade <- 0
for (row in 1:sizeA) {
  x <- abs(TeamA[row, "x"])
  y <- abs(TeamA[row, "y"])
  fgmade <- TeamA[row, "fgmade"]
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y < 7.8 & fgmade == 1) {
      sizeA_C3fgmade <- sizeA_C3fgmade + 1
    } 
}

APercentageC3_Made <- sizeA_C3fgmade / sizeA_C3
round(APercentageC3_Made, digits = 3)
```
APercentageC3_Made = 0.5

For Team B, what percentage of their shots were attempted in the 2PT zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q11}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamB <- filter(shots.df, team == "Team B")
sizeB <- nrow(TeamB)
sizeBTwoPt <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(x <= 22 & z <= 23.75) {
      sizeBTwoPt <- sizeBTwoPt + 1
    } 
}

BPercentage2PT <- sizeBTwoPt / sizeB
round(BPercentage2PT, digits = 3)
```
BPercentage2PT = 0.674

For Team B, what percentage of their shots were attempted in the NC3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q12}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamB <- filter(shots.df, team == "Team B")
sizeB <- nrow(TeamB)
sizeB_NC3 <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y > 7.8) {
      sizeB_NC3 <- sizeB_NC3 + 1
    } 
}

BPercentageNC3 <- sizeB_NC3 / sizeB
round(BPercentageNC3, digits = 3)
```
BPercentageNC3 = 0.277

For Team B, what percentage of their shots were attempted in the C3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q13}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamB <- filter(shots.df, team == "Team B")
sizeB <- nrow(TeamB)
sizeB_C3 <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y < 7.8) {
      sizeB_C3 <- sizeB_C3 + 1
    } 
}

BPercentageC3 <- sizeB_C3 / sizeB
round(BPercentageC3, digits = 3)
```
BPercentageC3 = 0.004

For Team B, what was the eFG in the 2PT zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q14}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamB <- filter(shots.df, team == "Team B")
sizeB <- nrow(TeamB)
#Could just include the two point field goals variable from Q11 here, but so the code chunk stands alone I will include this code again for this question
sizeBTwoPt <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(x <= 22 & z <= 23.75) {
      sizeBTwoPt <- sizeBTwoPt + 1
    } 
}

sizeB2PTfgmade <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  fgmade <- TeamB[row, "fgmade"]
  z <- sqrt(x^2 + y^2)
  if(x <= 22 & z <= 23.75 & fgmade == 1) {
      sizeB2PTfgmade <- sizeB2PTfgmade + 1
    } 
}

BPercentage2PT_Made <- sizeB2PTfgmade / sizeBTwoPt
round(BPercentage2PT_Made, digits = 3)
```
BPercentage2PT_Made = 0.444

For Team B, what was the eFG in the NC3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q15}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamB <- filter(shots.df, team == "Team B")
sizeB <- nrow(TeamB)
#Could just include the NC3 field goals variable from Q12 here, but so the code chunk stands alone I will include this code again for this question
sizeB_NC3 <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y > 7.8) {
      sizeB_NC3 <- sizeB_NC3 + 1
    } 
}

sizeB_NC3fgmade <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  fgmade <- TeamB[row, "fgmade"]
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y > 7.8 & fgmade == 1) {
      sizeB_NC3fgmade <- sizeB_NC3fgmade + 1
  } 
}

BPercentageNC3_Made <- sizeB_NC3fgmade / sizeB_NC3
round(BPercentageNC3_Made, digits = 3)
```
BPercentageNC3_Made = 0.339

For Team B, what was the eFG in the C3 zone? Rounded to 3 decimal places (e.g. 0.531).
```{r Q16}
#reading and filtering data in this chunk again so it may stand alone from the rest of the questions. 
shots.df <- read.csv("shots_data.csv", header = TRUE, as.is = TRUE)

TeamB <- filter(shots.df, team == "Team B")
sizeB <- nrow(TeamB)
#Could just include the C3 field goals variable from Q13 here, but so the code chunk stands alone I will include this code again for this question
sizeB_C3 <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y < 7.8) {
      sizeB_C3 <- sizeB_C3 + 1
    } 
}

sizeB_C3fgmade <- 0
for (row in 1:sizeB) {
  x <- abs(TeamB[row, "x"])
  y <- abs(TeamB[row, "y"])
  fgmade <- TeamB[row, "fgmade"]
  z <- sqrt(x^2 + y^2)
  if(z > 23.75 & y < 7.8 & fgmade == 1) {
      sizeB_C3fgmade <- sizeB_C3fgmade + 1
    } 
}

BPercentageC3_Made <- sizeB_C3fgmade / sizeB_C3
round(BPercentageC3_Made, digits = 3)
```
BPercentageC3_Made = 0
